Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-09 draft.tex
simplified knudsens theorem

\owen{Add remark that by Dunn's additivity theorem, the center has a natural $E_{n+1}$ algebra structure.}
\greg{I will add stuff and rewrite that later, hopefully to explain ``how'' to see the $E_{n+1}$-structure}

\greg{We could relate this to $P_n$-center of $\fg$. That shall also (but I have to think about the proof more), 
at least up to formality gives the $P_{n+1}$-structure on it. }

If $\epsilon: \fg \to 0$ is the trivial map, then we obtain the canonical augmentation $\epsilon: \UU_n \fg \to k$ of $\EE_n$ algebras.
In this case, we obtain a version of Koszul duality as the corollary.

@@

\greg{Somewhere we should recall that $\UU_n$ and its center are unoriented $\EE_n$ algebras and define factorization algebras over any manifold that came from the formula}

@@

\owen{Add overview}

@@

Although \cite{Knudsen} develops an adjunction between Lie and $\EE_n$ algebras \mahmoud{non-unital?}\greg{Both I think}\owen{augmented is probably best for us}
in any presentable symmetric monoidal stable $\infty$-category $\cC$,
we only work in the $\infty$-category of chain complexes $(\Mod_k, \otimes_k)$, 
where $k$ is a field of characteristic zero.
We summarize Knudsen's result in this setting as follows.

\begin{thm}\label{T:UnofLie}
There is a commuting square of adjunctions
\[
\begin{tikzcd}
\Alg_\Lie(\Mod_k) \arrow[r, bend left=20, shift left=.5ex,"\UU_n"] \arrow[dd] & \Alg_{\EE_n}(\Mod_k) \arrow[l, shift left=.5ex, "\oblv_n"] \arrow[dd]\\
&\\
\Mod_k \arrow[r, bend left=20, shift left=.5ex, "\Sigma^{1-n}"] \arrow[uu, bend left=20, shift left=.5ex, "\Free_\Lie"] & \Mod_k \arrow[l, shift left=.5ex,"\Sigma^{n-1}"] \arrow[uu, bend right=20, shift right=.5ex, "\Free_{\EE_n}"']
\end{tikzcd}
\]
\greg{Also explains what commutatrive means here ? Meaning the curved arrow diagram and the straight arrow diagram only; not combos of such}
\mahmoud{explain what oblv stands for}
where $\Sigma$ denotes suspension \owen{because tikzcd does weird things with ``[1-n]'' instead}, \mahmoud{earlier we denoted the shift by [n]. should we use $\Sigma^n$ everywhere?}.
(Curving arrows denote left adjoints.)

@@

The second part of this result leads to the explicit models in our theorems.

\owen{Add discussion of how this makes sense even on unoriented manifolds.}

In fact, Knudsen shows a stronger version of the second part.
if one restricts to working with open balls in $\RR^n$ (rather than arbitrary open sets)
then there is a $\Disk_n$-algebra ${\tt U}_n \fg$ assigning $\cliels(\fg[-n]) = \Sym(\fg[1-n])$ to each ball and it is manifestly locally constant.
This algebra ${\tt U}_n \fg$ is a model for~$\UU_n \fg$.

>>>>

\greg{We could relate this to $P_n$-center of $\fg$. That shall also (but I have to think about the proof more), 
at least up to formality gives the $P_{n+1}$-structure on it. }\owen{Brian now does this in the TFT section.}

If $\epsilon: \fg \to 0$ is the trivial map, then by taking the enveloping $\EE_n$ algebras, we obtain the canonical augmentation $\epsilon: \UU_n \fg \to k$ of $\EE_n$ algebras.
In this case, we obtain a version of Koszul duality as the corollary.

@@

@@

In this section we review key definitions and facts from the literature on $\EE_n$ and factorization algebras.

@@

Although \cite{Knudsen} develops an adjunction between Lie and augmented $\EE_n$ algebras
in any presentable symmetric monoidal stable $\infty$-category $\cC$,
we only work in the $\infty$-category of cochain complexes $(\Ch_k, \otimes_k)$, 
where $k$ is a field of characteristic zero.
We summarize Knudsen's result in this setting as follows.

\begin{thm}\label{T:UnofLie}
There is an adjunction of $\infty$-categories
\[
\begin{tikzcd}
\Alg_\Lie(\Ch_k) \arrow[r, bend left=20, shift left=.5ex,"\UU_n"]  & \Alg_{\EE_n}(\Ch_k) \arrow[l, shift left=.5ex, "\oblv_n"]
\end{tikzcd}
\]
where $\oblv_n$ denotes a ``forgetful'' functor from $\EE_n$ algebras to Lie algebras.

Both $\infty$-categories admit canonical forgetful functors to $\Ch_k$ and we denote both functors by $\oblv$;
these functors have left adjoints $\Free_\Lie$ and $\Free_{\EE_n}$, respectively.
There is a natural equivalence
\[
\UU_n (\Free_\Lie V) \simeq \Free_{\EE_n}(V[1-n])
\]
for every cochain complex~$V$.

@@

The final part of this result leads to the explicit models in our theorems.

\begin{rmk}
An appealing aspect of this result is that it makes manifest why such enveloping $\EE_n$ algebras determine factorization algebras on all $n$-dimensional manifolds, whether framed or oriented or unoriented.
The key point is that the model uses the compactly supported de Rham complex (or some other model of chains)
and hence makes sense on general manifolds.
\end{rmk}

In fact, Knudsen shows a stronger version of the second part.
if one restricts to working with open balls in $\RR^n$ (rather than arbitrary open sets)
then there is a $\Disk_n$-algebra ${\tt U}_n \fg$ assigning $\cliels(\fg[-n]) = \Sym(\fg[1-n])$ to each ball and it is manifestly locally constant.
This $\Disk_n$-algebra ${\tt U}_n \fg$ is another model for~$\UU_n \fg$.
